Portable Multi- and Many-Core Performance for Finite-Difference/Element Codes; Application to the Free-Surface Component of NEMO (NEMOLite2D 1.0).

### 2017-09-14 docs/papers/nemolite2d_performance/nemolite2d_perf.tex
nemolite-paper: mention PSyclone by name in related-approaches section

This paper is concerned with the implications of {PS}y{KA}l as a
design for architecting code. The implementation of an associated tool
for generating the middle, {PS}y, layer will be the subject of a future
paper. However, comparison with other approaches necessarily involves
tools rather than simply architectures.

>>>>

This paper is concerned with the implications of {PS}y{KA}l as a
design for architecting code. The implementation of an associated tool
(which we have named 'PSyclone') for generating the middle, {PS}y,
layer will be the subject of a future paper. However, comparison with
other approaches necessarily involves discussing other tools rather
than simply architectures.
